Using Deep Learning to Perform Fuzzy Joins

### 2018-10-22 old/paper/drlim.tex

\subsection{Dimensionality Reduction by Learning an Invariant Mapping}

The problem of dimensionality reduction, mapping a high dimensional group of entities onto a low dimensional manifold, is an important problem in many areas of machine learning. Dimensionality Reduction by Learning an Invariant Mapping is a technique for solving this problem by mapping points onto the manifold using a set of previously known matches and non-matches described by \cite{Hasdell:Siamese}. We used this technique not for reducing the dimensionality, but for logically mapping points onto a vector space. The goal of this technique is to minimize the distance between matched pairs and maximize the distance between unmatched pairs. This is accomplished using a network architecture know as a \textit{siamese} network. In this architecture there are two deep neural networks that share weights attached to a final layer that determines the distance between the output of the two hidden networks and minimizes the loss function. To train the network a set of matched and non-matched pairs of inputs is sent through the network and the weights are adjusted to maximize or minimize distance accordingly. This is accomplished using the following loss function \[ L(W, Y, \vec{X}_1, \vec{X}_2) = (1 - Y)\frac{1}{2}(D_W)^2 + (Y)\frac{1}{2}\{max(0, m - (D_W))\}^2\] Where \(D_W\) is the euclidean distance between the two outputs, \textit{m} is a radius beyond which we ignore dissimilar points, and Y is the similar or dissimilar label.

>>>>

\subsection{Siamese Network}

 A method for logically mapping a set of points onto a manifold using a set of previously known matches and non-matches is described by \cite{Hasdell:Siamese}. The goal of this technique is to minimize the distance between matched pairs and maximize the distance between unmatched pairs. This is accomplished using a network architecture know as a \textit{Siamese} network. In this architecture there are two deep neural networks that share weights attached to a final layer that determines the distance between the output of the two hidden networks and minimizes the loss function. To train the network a set of matched and non-matched pairs of inputs is sent through the network and the weights are adjusted to maximize or minimize distance accordingly. This is accomplished using the following loss function \[ L(W, Y, \vec{X}_1, \vec{X}_2) = (1 - Y)\frac{1}{2}(D_W)^2 + (Y)\frac{1}{2}\{max(0, m - (D_W))\}^2\] Where \(D_W\) is the euclidean distance between the two outputs, \textit{m} is a radius beyond which we ignore dissimilar points, and Y is the dissimilar label.

### 2018-10-22 old/paper/paper.tex

\end{enumerate} 
Even using these three rules in combination resulted in too many false negatives. Therefore we decided to treat all matches resulting from any of the three rules as valid.
\input{drlim}
\input{Aproximate_Nearest_Neighbors}
\input{Triplet_loss}
\input{LSTM}
\section{Experiments}
\subsection{Rule Based}
If we treat it as a success if there is a correct match in any of the first three slots, we get an F\textsubscript{1} score of 0.7. Since the issue is mostly false negatives, and therefore even some of the first three slots were often empty, so even if we accept any of the top 1000 as a success, we get FSCORE2, not much better.
\input{siamese_exper}
\section{Conclusions}
While we have a very good machine learning based matcher, that does not appear to translate into very good blocking. We still need to explore why we only getting around 69\% of the matches in the top 40 items, when we have the positive closer than the negative in 97\% of cases.  
%\end{document}  % This is where a 'short' article might terminate

>>>>

\end{enumerate} 
Even using these three rules in combination resulted in too many false negatives. Therefore we decided to treat all matches resulting from any of the three rules as valid.
\input{drlim}
\input{Aproximate_Nearest_Neighbors}
\input{Triplet_loss}
\input{LSTM}
\section{Experiments}
\subsection{Rule Based}
To test the rule based matcher we ran the blocker followed by the matcher and calculated F-scores based on how many correct matches were in the top 3. We got an F-score of 0.6. Since the issue is mostly false negatives, and therefore even some of the first three slots were often empty, so even if we accept any of the top 1000 as a success, we get an F-score of 0.63, not much better.
\input{siamese_exper}
\section{Conclusions}
While we have a very good machine learning based matcher, that does not appear to translate into very good blocking. We still need to explore why we only getting around 69\% of the matches in the top 40 items, when we have the positive closer than the negative in 97\% of cases.  
%\end{document}  % This is where a 'short' article might terminate
